The journey of Multiple Sequence Alignment

### 2021-08-05 MSA_Notum_journey.Rmd
tblastn sequences

>>>>

# Search four "representative" proteins that have the WIF domain respect to sponges
In the tree of WIF from oma.db we can see 4 big clusters that have particular characteristics
One is the cluster of the Human WIF (HS|WIF1) the the human with RYK domain (Hs|RYK) then those with 
NTR domain and then those with the "pure"  PK_TYR_SER_THR_PKinase
We will tblastn from each cluster one and evaluate some of the results
## The selected sequences:

### Hs|WIF1 
```{bash}
>Hs|WIF1 gi|111125011|ref|NP_009122.2| gi|111125011|ref|NP_009122.2| wnt inhibitory factor 1 precursor [Homo sapiens]
MARRSAFPAAALWLWSILLCLLALRAEAGPPQEESLYLWIDAHQARVLIGFEEDILIVSEGKMAPFTHDFRKAQQRMPAI
PVNIHSMNFTWQAAGQAEYFYEFLSLRSLDKGIMADPTVNVPLLGTVPHKASVVQVGFPCLGKQDGVAAFEVDVIVMNSE
GNTILQTPQNAIFFKTCQQAECPGGCRNGGFCNERRICECPDGFHGPHCEKALCTPRCMNGGLCVTPGFCICPPGFYGVN
CDKANCSTTCFNGGTCFYPGKCICPPGLEGEQCEISKCPQPCRNGGKCIGKSKCKCSKGYQGDLCSKPVCEPGCGAHGTC
HEPNKCQCQEGWHGRHCNKRYEASLIHALRPAGAQLRQHTPSLKKAEERRDPPESNYIW
```

### Hs|RYK
```{bash}
>Hs|RYK gi|54607020|ref|NP_001005861.1| gi|54607020|ref|NP_001005861.1| tyrosine-protein kinase RYK isoform 1 precursor [Homo sapiens]
MRGAARLGRPGRSCLPGARGLRAPPPPPLLLLLALLPLLPAPGAAAAPAPRPPELQSASAGPSVSLYLSEDEVRRLIGLD
AELYYVRNDLISHYALSFSLLVPSETNFLHFTWHAKSKVEYKLGFQVDNVLAMDMPQVNISVQGEVPRTLSVFRVELSCT
GKVDSEVMILMQLNLTVNSSKNFTVLNFKRRKMCYKKLEEVKTSALDKNTSRTIYDPVHAAPTTSTRVFYISVGVCCAVI
FLVAIILAVLHLHSMKRIELDDSISASSSSQGLSQPSTQTTQYLRADTPNNATPITSSLGYPTLRIEKNDLRSVTLLEAK
GKVKDIAISRERITLKDVLQEGTFGRIFHGILIDEKDPNKEKQAFVKTVKDQASEIQVTMMLTESCKLRGLHHRNLLPIT
HVCIEEGEKPMVILPYMNWGNLKLFLRQCKLVEANNPQAISQQDLVHMAIQIACGMSYLARREVIHKDLAARNCVIDDTL
QVKITDNALSRDLFPMDYHCLGDNENRPVRWMALESLVNNEFSSASDVWAFGVTLWELMTLGQTPYVDIDPFEMAAYLKD
GYRIAQPINCPDELFAVMACCWALDPEERPKFQQLVQCLTEFHAALGAYV
```

### Of|1176102141
```{bash}
>Of|1176102141 XP_020621816.1| uncharacterized protein LOC110059462 [Orbicella faveolata]
MAGLEARNFLKVLFLMSVPVLGKCSTKLNVFLDAREVSRFLYDLNTNLFLVQDGVVAPILKTPILSSMIPPIEPYIKDLK
FKFNATGMVQYSLNFKSSNETIMKHPTANIRLNGLVPRKTKVFRVKFPCTGKVIGGVLLTINISFVDVAGSEIWGPLSLT
LKRQCVSGNDDLINRYNSTESGEVSPLPAPQICNKRCSKRHVMRRFCLSDFVIKARMESEVMRNGLPRLRLRIARTYKQG
KVKINNKNQLMEKRGQEITCSCSNLKVNKVYLILGKEDKRKRVLFLDNFSTALEWNKNGKSYVKTFRNRSSCPERKMP
```

### Ci|198430807
```{bash}
>Ci|198430807 ref|XP_002129769.1| PREDICTED: tyrosine-protein kinase RYK [Ciona intestinalis]
MRVCAYILAVVLLPCMSKCSIDLYLAEDQVEKLFGIADAEMYYIRNGIINENAVNFVAHVQPEHTDLTYLWKVTNKAITV
AYDLDILDVQKSPAQLNTGSVEMNKHSILYPPKLESKSGTIRYSEDLQPQTLKVSLVCTGEREGNVTVTMKLKLVMDSGT
DLVVNIKRLKKCLKTHSFVEDKPVLTDQPSEPNDQDLNLGGTQQSTSAFYISVSVVSSFIVLIVVGVTLWHVRMSKRYQR
SGVDNCIPMQPGAQHLNQFLRPDLPNNALKPPSHSSLMQIITPLINDLGTDINEIQSKLSAIAIPRENVDIGELTLKGTF
ARIYKGTLDDGTPVLIKTVSDMATEEQKRLLLFESSLLRGMHHRNLLSMKHVVLQDDSTPPMVLFHFMEGGNLKHYLQGL
KLKESPGLVSGIFGSGSTKYEQVSTQDLVEMAIQIACGMTYLSKRGLVHKDLAARNCVIDRDLKVKISDNALSRDAFPAD
YCCLGDNENRPVRWLGLESLVHKVYSSASDVWSFGVLLWELQSLAATPYADIDDFEMASYLKDGFRLSQPINCPDHLYSI
IASCWHYSPDQRPSFTKLLQMLTEFYAELEVYV
```
